Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v2.0/abstract.tex
Add new version of the paper

A generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high intensity electromagnetic field is presented.
The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems. Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using a strong external light.
Our results align with well-established and experimentally
verified theoretical descriptions for undressed systems while providing a more generalized analysis on the conductivity characterstics in quantum Hall systems.
Thus, our model can be applied to accurately interpret the usage of external strong radiation as a tool in nanoscale quantum devices.

>>>>

We present a generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high-intensity electromagnetic field.
The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure.
Moreover, the Floquet-Fermi golden rule is adopted to explore the impurity scattering effects on charge transport in disordered quantum Hall systems.
We derive fully analytical expressions to describe longitudinal components in the conductivity tensor in dressed quantum Hall systems. Subsequently, we demonstrate that the conductivity characteristics of quantum Hall systems can be manipulated using a strong external light.
Our results align with well-established and experimentally
verified theoretical descriptions for undressed systems while providing a more generalized analysis of the conductivity characteristics in quantum Hall systems.
Thus, our model can be applied to accurately interpret the usage of  strong external radiation as a tool in nanoscale quantum devices.

### 2021-08-16 paper/v2.0/sections/1_introduction.tex
Add new version of the paper

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}. However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
In these instances, a more accurate treatment needs to adopt. Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}. Here the applied high-intensity  electromagnetic field identify as the dressing field.

Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form. In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula. This opened the path to explore and exploit the charge transport attributes of nanostructures under an intense dressing field.

@@

In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening agaist Fermi level for each Landau levels and provide less agreement with the empirical results.

@@

The paper is organized as follows. In Sec.  \ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conlusions.

>>>>

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Most recent studies on the subject have considered the driving field as a perturbation field \cite{pervishko15,morina15}. However, this assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher-order terms influence the physics more strongly and the basis of the perturbative treatment begins to break down.
In these instances, a more accurate treatment needs to adopt. Thus, we treat the interacting fermion system and the radiation as one combined quantum system, namely dressed system \cite{morina15,cohen98,scully01}. Here the applied high-intensity  electromagnetic field identify as the dressing field.

Theoretical analyses on the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for conductivity in a dressed system has been derived in a fully closed analytical form. In their study, a novel type of Green’s functions, namely four-times Green’s functions were used to derive the Floquet-Drude conductivity formula. This opened the path to exploring and exploiting nanostructures' charge transport attributes under an intense dressing field.

@@

In contrast, more exciting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.

@@

The paper is organized as follows. Sec.  \ref{sec_schrodinger_problem} introduces our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory} provides the Floquet theory interpretation of these wave functions.
We introduce Floquet-Fermi golden rule for a quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoretical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}.
In Sec. \ref{sec_conclusions}, we summarize our analysis and present our conclusions.

### 2021-08-16 paper/v2.0/sections/2_schrodinger_problem.tex
Add new version of the paper

Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space. In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{\text{T}}$ which is pointed towards the $z$ axis. In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface. We specially select the frequency of the dressing field $\omega$ to be in the off-ersonant regime such that the field behaves as a purely dressing field. Furthermore, without limiting the generality we choose $y$-polorized electric field $\vb{E} = (0,E\sin(\omega t),0)^{\text{T}}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
\begin{figure}[b]
\includegraphics[scale=0.9]{figures/fig_1}
\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and dressing field (with y-polarized electric field $\vb{E}$) are applied perpendicular to the surface of 2DEG.}
\end{figure}
Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field respectively.

Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$. Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}. Thus, our system can be represented with a time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\text{T}}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs. \cite{husimi53,ditt98,dini16}. Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\big(y - y_0 - \zeta(t)\big)\\
    & \quad\times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_n t
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    & \quad+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$. Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant. The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
For details of the full derivation refer to Appendix \ref{appendix_a}.
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system. Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

>>>>

Our system consists of a 2DEG placed on the $xy$-plane of the three-dimensional coordinate space. In our analysis, the 2DEG is subjected to a nonoscillating magnetic field $\vb{B} = (0,0,B)^{T}$, which is pointed towards the $z$-axis. In addition, a linearly polarized strong light is applied perpendicular to the 2DEG surface. We specially select the frequency of the dressing field $\omega$ to be in the off-resonant regime such that the field behaves as a purely dressing field. Furthermore, without limiting the generality, we choose a $y$-polarized electric field $\vb{E} = (0,E\sin(\omega t),0)^{T}$ for the linearly polarized dressing field (Fig.~\ref{fig_1}).
\begin{figure}[b]
\includegraphics[scale=0.9]{figures/fig_1}
\caption{\label{fig_1} Our 2DEG system only confined in the $(x,y)$ plane while both stationary magnetic field $\vb{B}$ and dressing field (with y-polarized electric field $\vb{E}$) are applied perpendicular to the surface of 2DEG.}
\end{figure}
Here $B$ and $E$ represent the amplitudes of the stationary magnetic field and oscillating electric field, respectively.

Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$. Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}. Thus, we can represent our system with a time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{T}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{T}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs. \cite{husimi53,ditt98,dini16}. Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\big(y - y_0 - \zeta(t)\big)\\
    & \quad\times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_n t
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    & \quad+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$. Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant. The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
Moreover, $\chi_n$ are well-known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
For details of the full derivation refer to Appendix \ref{appendix_a}.
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system. Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

### 2021-08-16 paper/v2.0/sections/3_floquet_theory.tex
Add new version of the paper

Symmetry conditions often gives useful insights into the behaviors of physical quantum systems.
For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was emplyoed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time dependent part and a periodic time dependent part, we present the quasienergies as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which only depends on a single quantum number $n$. The Floquet modes can then be recognized as
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8a}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq_8b}
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}. Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.

Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we have introduced new parameters
\begin{equation} \label{eq_11a}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq_11b}
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For a detailed derivation, refer to Appendix \ref{appendix_b}. Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

>>>>

Symmetry conditions often give useful insights into the behaviors of physical quantum systems.
For instance, in the famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation for quantum systems occupying a discrete translational symmetry in the configuration space. Similarly, Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}.
The Floquet-Drude conductivity theory was employed recently by Wackerl \textit{et al.} \cite{wackerl20} as a method to analyze the transport properties of quantum systems exposed to strong radiation.
In their work, they have presented more accurate results than the former theoretical descriptions for the conductivity of nanoscale systems in the  presence of a dressing field. Therefore, we apply the Floquet-Drude conductivity theory to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

First, we need to identify the \textit{quasienergies} and time periodic \textit{Floquet modes} \cite{grifoni98} for the wave functions given in Eq.~(\ref{eq_2}). By factorizing the wave function into a linearly time-dependent part and a periodic time-dependent part, we present the quasienergies as
\begin{equation} \label{eq_6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
which only depends on a single quantum number $n$. The Floquet modes can then be recognized as
\begin{equation} \label{eq_7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) = &
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg),
  \end{aligned}
\end{equation}
with
\begin{equation} \label{eq_8a}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq_8b}
  \xi = \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t).
\end{equation}
For a detailed derivation, refer to Appendix \ref{appendix_b}.
It is important to note that these Floquet modes are time-periodic ($T=2\pi/\omega$) functions. At resonance $\omega = \omega_0$, the energy levels occupy a continuous spectrum and the quasienergy formalism is no longer valid \cite{popov70}. Therefore, in this work we choose a dressing field frequency obeying the condition $\omega \neq \omega_0$.

Performing the Fourier transform over the confined 2D space, we obtain the momentum space ($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we have introduced new parameters
\begin{equation} \label{eq_11a}
  b =
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)},
\end{equation}
and
\begin{equation} \label{eq_11b}
  d =
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written as Floquet states in momentum space as
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}
